Hydras \& Co.

### 2022-03-15 doc/part-hydras.tex
corrections chapter 3 (up to p. 63)

\begin{itemize}
\item A ``mathematical'' representation of the set of countable ordinal numbers, after Kurt Schütte~\cite{schutte}. This representation uses several (hopefully harmless) axioms. We use it as a reference for proving the correctness of ordinal notations.
\item A family of \emph{ordinal notations} (also called \emph{[ordinal] notation systems}), \emph{i.e.} data types used to represent segments $[0,\mu)$, where $\mu$ is some countable ordinal. Each ordinal notation is defined inside the Calculus of Inductive Constructions (without axioms). Many functions are defined, allowing proofs by computation. Note that proofs of 
correctness of a given ordinal notation with respect to Schütte's model obviously use axioms.
Please execute the \texttt{Print Assumptions} command in case of doubt.
\end{itemize}

@@

It is interesting to compare proofs of a given property (for instance the associativity of addition) both in the computational framework of some ordinal notation, and in the axiomatic model of Schütte.

@@

Such a structure can be proved correct relatively to a bigger ordinal notation or
to Schütte's model.

@@

@@

\inputsnippets{ON_plus/compareDef,
  ON_plus/compareCorrect, ON_plus/plusComp}

The Lemma \texttt{Wellfounded.Disjoint\_Union.wf\_disjoint\_sum} of Standard Library
helps us to prove that our order \texttt{lt} is well-founded, thenwe can build an instance of \texttt{ON}:

@@

\inputsnippets{ON_Omega2/Omega2Def, ON_Omega2/Defs}

@@

\subsection{A proof of termination using \texorpdfstring{$\omega^2$}{omega^2}} 
\label{sect:merge-example}.

@@

\textbf{Hint:} You may add to your function a third argument usually called \texttt{fuel} for allowing you to give a structurally 
recursive function (\emph{cf} the post of Guillaume Melquiond on Coq-club (Dec 21, 2020)
\url{https://sympa.inria.fr/sympa/arc/coq-club/2020-12/msg00069.html}).
The type \texttt{fuel}, an alternative 
to \texttt{nat} is available on \href{../theories/html/hydras.Prelude.Fuel.html}{Prelude.Fuel}).
%\index{coq}{Giving fuel to a long computation}

>>>>

\begin{itemize}
\item A ``mathematical'' representation of the set of countable ordinal numbers, after Kurt Schütte~\cite{schutte}. This representation uses several (hopefully harmless) axioms. We use it as a reference for proving the correctness of ordinal notations.
  We are also progressively importing \gaia's~\cite{Gaia} definitions and theorems, based on Bourbaki's set theory~\cite{Grimm2016}. Chapter~\ref{gaia-chapter} is dedicated to the connexion between libraries \HydrasLib and \gaia.

\item A family of \emph{ordinal notations} (also called \emph{[ordinal] notation systems}), \emph{i.e.} data types used to represent segments $[0,\mu)$, where $\mu$ is some countable ordinal. Each ordinal notation is defined inside the Calculus of Inductive Constructions (without axioms). Many functions are defined, allowing proofs by computation. Note that proofs of 
correctness of a given ordinal notation with respect to Schütte's model obviously use axioms.
Please execute the \texttt{Print Assumptions} command in case of doubt.
\end{itemize}

@@

It is interesting to compare proofs of a given property (for instance the associativity of addition) both in the computational framework of some ordinal notation, and in mathematical  models
of Schütte or \gaia.

@@

Such a structure may be proved correct relatively to a bigger ordinal notation or to Schütte's or \gaia's model.

@@

%\pagebreak

@@

\inputsnippets{ON_plus/compareDef, ON_plus/compareCorrect}
\inputsnippets{ON_plus/plusComp}

Standard library's lemma \texttt{Wellfounded.Disjoint\_Union.wf\_disjoint\_sum} 
is applied  to prove that our order \texttt{lt} is well-founded, allowing us to build an instance of \texttt{ON}:

@@

\inputsnippets{ON_Omega2/Omega2Def, ON_Omega2/Defs}
\inputsnippets{ON_Omega2/Ex1}

@@

\subsection{A proof of termination using \texorpdfstring{$\omega^2$}{omega^2}} 
\label{sect:merge-example}

@@

\textbf{Hint:} You may add to your function a third argument usually called \texttt{fuel} for allowing you to give a structurally 
recursive function (\emph{cf} the post of Guillaume Melquiond on Coq-club (Dec 21, 2020)
\url{https://sympa.inria.fr/sympa/arc/coq-club/2020-12/msg00069.html}).
The type \texttt{fuel}, an alternative 
to \texttt{nat} is available on \href{../theories/html/hydras.Prelude.Fuel.html}{Prelude.Fuel})
.
%\index{coq}{Giving fuel to a long computation}
